### 2014-09-03 tex/javalite.tex
Fixed some typos in the javalite and precise rules figures.

The heap is a labeled bipartite graph consisting of references,
$\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine syntax in
\figref{fig:machine-syntax} defines that graph in $\cfgnt{L}$, the
location map, and $\cfgnt{R}$, the reference map. As done with the
environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial
functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
of location-constraint pairs in the heap associated with the given
reference, and$\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
reference associated with the given location-field pair in the
heap.

>>>>

The heap is a labeled bipartite graph consisting of references,
$\cfgnt{r}$, and locations, $\cfgnt{l}$. The machine syntax in
\figref{fig:machine-syntax} defines that graph in $\cfgnt{L}$, the
location map, and $\cfgnt{R}$, the reference map. As done with the
environment, $\cfgnt{L}$ and $\cfgnt{R}$ are treated as partial
functions where $\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the set
of location-constraint pairs in the heap associated with the given
reference, and $\cfgnt{R}(\cfgnt{l},\cfgnt{f}) = \cfgnt{r}$ is the
reference associated with the given location-field pair in the
heap.
